Revisiting the hydrodynamic modulation of short surface waves by longer waves

### 2024-09-30 paper/paper.tex
Near-final edits to the text

\title{Revisiting the hydrodynamic modulation of short waves by longer waves}

@@

\begin{equation}
\label{eq:wave_action2}
\dfrac{\partial N}{\partial t}
+ \left(C_g + U\right) \dfrac{\partial N}{\partial x}
+ N \dfrac{\partial U}{\partial x}
+ N \dfrac{\partial C_g}{\partial x}
= 0
\end{equation}
This equation is similar to (\ref{eq:wavenumber}), except for the last term
which represents the inhomogeneity of the group speed.
As \citet{peureux2021unsteady} explained, the presence of this term causes
unstable growth of wave action in infinite long-wave trains.
(\ref{eq:wavenumber}) and (\ref{eq:wave_action2}) are the governing equations
that we approximate and solve analytically in \S\ref{section:analytical_solutions},
and numerically in their full form in \S\ref{section:numerical_solutions}.

@@

The first set of simulations is performed for the long-wave steepness of
$\varepsilon_L = 0.1$, $0.2$, and $0.4$ (Fig. \ref{fig:numerical_solutions}).
The long-waves are initialized from rest ($a_L = 0$) and are ramped up
to their target steepness after 5 long-wave periods, thus mimicking the
passage of a long-wave group
(we explain in more detail the importance of ramping up the long-wave forcing
in the next subsection).
At $\varepsilon = 0.1$, the numerical solutions for the wavenumber, amplitude,
and steepness modulation are all remarkably similar to the analytical solutions
(Fig. \ref{fig:numerical_solutions}a,d,g).
This suggests that at low long-wave steepness that steady analytical solution
is a reasonable proxy for the fully-nonlinear crest-action conservation
equation solutions.
The numerical solutions diverge more notably from the analytical ones at
moderate steepness of 0.2 (Fig. \ref{fig:numerical_solutions}b,e,h), and are
considerably different at very high steepness of 0.4
(Fig. \ref{fig:numerical_solutions}c,f,i).
These differences suggest that at high steepness the inhomogeneity of
gravitational acceleration and group speed become important.

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/numerical_vs_analytical_solutions_with_phase.png}
\caption{
  Comparison of numerical solutions of wavenumber, amplitude, and steepness modulation
  with their analytical solutions, for $\varepsilon_L$ = 0.1, 0.2, and 0.4.
}
\label{fig:numerical_solutions}
\end{figure}

The maximum modulations of the short-wave wavenumber, amplitude, and steepness
from the analytical and numerical solutions, are shown on Figs.
\ref{fig:numerical_vs_analytical_k},
\ref{fig:numerical_vs_analytical_a}, and
\ref{fig:numerical_vs_analytical_ak}, respectively, as function of the long-wave
steepness $\varepsilon_L$.
Overall, the numerical solutions, based on the linear and third-order Stokes long wave
alike, begin to diverge from the analytical solution at $\varepsilon_L \approx 0.2$.
The numerical solution using the Stokes long wave is quantitatively very similar
to the fully-nonlinear solutions of \citet{longuet1987propagation} in amplitude
modulation, however with somewhat lower wavenumber and steepness modulations.
For example, at $\varepsilon_L = 0.4$, the steepness modulation in our solutions
is close to 6, whereas \citet{longuet1987propagation} finds it close to 8.
The underestimate in the wavenumber modulation at high long-wave steepness
relative to the results of \citet{longuet1987propagation}
is likely due to his long wave velocities being evaluated to a higher order
than they are here.
Nevertheless, the overall steepness modulation between the two numerical
approaches are remarkably similar, and either solution would cause the
short-waves of even low steepness to break \citep{banner1993wave}.

@@

The key result of \citet{peureux2021unsteady} is that of unsteady steepening of
short waves when a homogeneous field of short waves is forced by an infinite
long-wave train.
The steepening is driven by the progressive increase in the action of short
waves (as opposed to their wavenumber), and is centered on the group of short
waves that begins its journey in the trough of the long wave.
This is because the unmodulated short waves that begin their journey in the
trough first enter the convergence region before reaching the divergence region.
Inversely, the short waves that begin around the crest of the long-wave first
enter the divergence region and will thus have their action and wavenumber
decreased.
We reproduce this behavior in Fig. \ref{fig:modulation_3panel_infinite}, which
shows the evolution of the short-wave action, wavenumber, and steepness
modulation (here defined as the change of a quantity relative to its initial value).
The long waves have $\varepsilon_L = 0.1$ and $k_L = 1$, and the short waves
have $k = 10$.
After 10 long-wave periods, the short-wave action modulation $\widetilde{N}/N$
is approximately doubled, consistent with the unsteady growth reported by
\citet{peureux2021unsteady}.
Another important property of this solution is that the short-wave group that
experiences peak amplification (dampening) are not locked in to the long-wave
crests (troughs), as they are in the solution by \citet{longuet1960changes}.

@@

Why does this unsteady growth of short-wave action occur?
As \citet{peureux2021unsteady} explain, "the additional change in advection
velocity due to the modulation of the short wave group speed gives an additional
amplification."
That is, it is the inhomogeneity term $N \dfrac{\partial C_g}{\partial x}$ that
is responsible for the instability.
However, the instability only occurs if the short waves are initialized as a
uniform field.
If they are initialized instead as a periodic function of the long-wave phase
such that their wavenumber (and optionally, action) is higher on the crests
and lower in the troughs, akin to the prior steady solutions, the instability
does not occur.

@@

Why is it, then, that the solution for short-wave modulation is not only
quantitatively, but also qualitatively, different depending on the short-wave
initial conditions?
It may at first seem that there is something special about the uniform initial
conditions that makes its solutions grow unsteadily and indefinitely.
\citet{peureux2021unsteady} described this scenario as "...the sudden appearance
of a long wave perturbation in the middle of a homogeneous short wave field".
However, such a scenario is not realistic in the ocean where waves tend to
organize into groups due to their dispersive nature.
To test whether it is the sudden onset of long-wave forcing that causes the
unstable growth, we repeat the numerical simulation of Fig.
\ref{fig:modulation_3panel_infinite}, except for a linear ramp applied to $a_L$
(and consequently, $U$ and $W$ as well) for the first five periods:
$a_L(t) = min(a_L, a_L t / \left(5 T_L\right))$, where $T_L$ is the long-wave period.
This result is shown in Fig. \ref{fig:modulation_3panel_ramp}.
The key distinction that arises with the introduction of the ramp is that the
modulation pattern of short waves is now locked in with the long-wave crests,
and their indefinite steepening vanishes.
The stabilization effect of the long-wave ramp is more readily assessed in
Fig. \ref{fig:unsteady_growth_timeseries}, which shows the maximum short-wave
steepness modulation as function of time over 30 long-wave periods, for the
infinite long-wave train case and that when applying the linear ramp to the
long-wave forcing.
Comparing the wave action propagation ($C_g \frac{\partial N}{\partial x}$) and
inhomogeneity ($N \frac{\partial C_g}{\partial x}$) tendencies reveals that
after only one long-wave period, the propagation and inhomogeneity tendencies
are unbalanced and amplify the steepening of short waves
(Fig. \ref{fig:inhomogeneity_tendencies}).
Although \citet{peureux2021unsteady} correctly pointed out that the unstable
growth of short-wave steepness occurs due to the resonance of the inhomogeneity
tendency with the short-wave action perturbation, in case of a gentle ramp
up of the long-wave forcing, the propagation and inhomogeneity tendencies
mostly balance each other out, thus allowing the short-wave steepening to
lock in to the long-wave crests.

@@

We now proceed to examine the numerical solutions with the long-wave forcing
applied as a long-wave group.
The wave group is simulated as a non-dispersive train of long waves whose
amplitude scales with $\cos{2 \pi t / (N T_L)}$, where $N$ is the number of
long waves in the group.
The elevation of the long waves thus gradually ramps up from rest to $a_L$ at
$t = N/2 T_L$, after which it gradually decreases toward zero.
In this simulation, $N = 10$ and $\varepsilon = 0.1$ as in the previous two
simulations.
The modulations of short-wave wavenumber, amplitude, and steepness in response
to such long-wave group is shown in Fig. \ref{fig:modulation_3panel_groups}.
Like in the case of a linear ramp, the modulation pattern here is locked in to
the long-wave crest and peaks at approximately 1.2 for short-wave steepness.
After the peak of the long-wave group passes, the short-wave modulation recedes
back toward the resting state.

@@

The solutions presented here, analytical and numerical alike, are valid only
for certain scales of short and long waves.
Specifically, the wave action conservation equation, introduced by
\citet{bretherton1968wavetrains}, requires that the ambient velocity is slowly
varying on the time scales of short waves, \textit{i.e.}
$|\partial U / \partial x| \ll k |U|$
and $|\partial U / \partial t| \ll \sigma |U|$.
This implies $k_L \ll k$ and $|\sigma_L| \ll \sigma|$, respectively.
Another requirement is for the short-waves to remain linear, which implies
$a k \ll 1$.
Furthermore, the short waves examined here do not include the effects of
surface tension (gravity-capillary waves) or intermediate or shallow water.
Within these limits, the crest-action conservation equations provide an
elegant and relatively simple framework to study the hydrodynamic modulation
of short waves by longer waves.
This approach, of course, isolates this particular process from others
dominant modulation and nonlinear transfer processes, such as wave growth
by wind, wave dissipation, and aerodynamic sheltering by the longer waves.

Although in this paper we only explored the wavenumbers 1 and 10 for the long
and short waves, respectively ($k/k_L = 10$), the results are not sensitive
to different values of $k_L$, provided that the amplitude $a_L$ is set such that
the long-wave steepness $\varepsilon_L = a_L / k_L$ is the same.
Numerical simulations with that compare $k/k_L = 10$ and $k/k_L = 100$ show
very little sensitivity $k/k_L$ (not shown), consistent with the results of
\citet{longuet1987propagation}.
Specifically, the short-wave steepness modulation is 1\% larger at
$\varepsilon_L = 0.27$ for $k/k_L = 10$ compared to $k/k_L = 100$, and 4\%
larger at $\varepsilon_L = 0.4$.
This suggests that as long as $k/k_L \gg 1$, the modulation amplitude is
largely independent of the ratio $k/k_L$.

Despite several studies that provided qualitatively similar steady solutions
for the short-wave modulation by long waves
\citep{longuet1960changes,phillips1981dispersion,longuet1987propagation,henyey1988energy,zhang1990evolution},
it was not obvious from the governing equations that the fully-nonlinear
steady solutions should exist.
\citet{peureux2021unsteady} examined this problem numerically and found that
the solutions are stable only if the short-wave field is initialized from
a prior steady solution of the form of that from \citet{longuet1960changes}.
If the short-wave field is instead initialized from a uniform field, they
found that the short-wave amplitude, and thus steepness as well, grow
unsteadily.
However, in this study we demonstrate that the unsteady steepening of short
waves only occurs in the case of a sudden appearance of long waves, where
the velocity fields induced by the long waves act in their full capacity
on the short waves that have not yet had time to "lock in" to the long-wave
crests.
In such a hypothetical scenario, sudden forcing on short waves causes the
modulation pattern to detach itself from the long-wave crests and to propagate
at the short-wave group speed.
When this occurs, the modulated short-waves are no longer in a stabilizing
resonance with the surface convergence and divergence induced by the long-wave
orbital velocity, and each long-wave passage further destabilizes the short-wave
field, causing it to steepen indefinitely.

Another important consideration of the hydrodynamic modulation process is
whether it should somehow be accounted for in phase-averaged spectral wave
models \citep{group1988wam,tolman1991third,donelan2012modeling} used for global
and regional wave forecasting.
In the early days of spectral wave modeling, \citet{willebrand1975energy}
examined the effect of a wave spectrum on the short-wave group velocity,
and found the effect of up to several percent modulation.
For a practical implementation in a spectral wave model, this would have to
incur an additional loop over all frequencies for each short-wave frequency.
It was thus not deemed practical to include this effect in wave models at the time.
However, with the recent advances in machine learning and phase-resolving modeling
of short waves, the effect of wave-modulation deserves re-examination.

TODO Implications for spectral wave models and wind input to short waves.

@@

In this paper we revisited the problem of short-wave modulation by long waves
from a linear wave theory perspective.
Using the linearized wave crest and action conservation equations coupled with
nonlinear solutions for the effective gravity, we derived steady analytical
solutions for the modulation of short wave wavenumber, amplitude, steepness,
intrinsic frequency, and phase speed.
The latter two have not been previously examined in the context of short-wave
modulation, but are important for correctly calculating the wind input into
short waves, which is proportional to the wind speed relative to the wave
celerity.
The approximate steady solutions yield higher wavenumber and amplitude
modulation than that of \citet{longuet1960changes}, and somewhat lower than 
the numerical solutions of \citet{longuet1987propagation} and
\citet{zhang1990evolution}.
This is mainly due to the analytical solution requiring the crest and action
conservation equations to be linearized, and the nonlinearity arising due
to the evaluation of short waves on the surface of the long wave (as opposed to
the mean water level) and due to nonlinear effective gravity.

The numerical solutions of the full wave crest and action conservation equations
are consistent with the analytical solutions for $\varepsilon_L < 0.2$.
The simulations also reveal that the unsteady growth of short-wave steepness
reported by \citet{peureux2021unsteady} is due to the sudden appearance of
long waves in a homogeneous short-wave field, a scenario that is unlikely to
occur in the open ocean.
A more likely condition such as that of a long-wave groups, are only mildly
destabilizing for the short waves.
These results suggest that for mildly-to-moderately steep short waves,
the analytical steady solutions presented here are sufficient to describe the
modulation of short waves by long waves.

>>>>

\title{Revisiting the hydrodynamic modulation of short surface waves by longer waves}

@@

\begin{equation}
\label{eq:wave_action2}
\dfrac{\partial N}{\partial t}
+ \left(C_g + U\right) \dfrac{\partial N}{\partial x}
+ N \dfrac{\partial U}{\partial x}
+ N \dfrac{\partial C_g}{\partial x}
= 0
\end{equation}
This equation is similar to (\ref{eq:wavenumber}), except for the last term
which represents the inhomogeneity of the group speed.
As \citet{peureux2021unsteady} explained, the presence of this term causes
unstable growth of wave action in infinite long-wave trains.
(\ref{eq:wavenumber}) and (\ref{eq:wave_action2}) are the governing equations
that we approximate and solve analytically in \S\ref{section:analytical_solutions},
and numerically in their full form in \S\ref{section:numerical_solutions}.
It is worth noting that this system of equations is semi-coupled, meaning that
it is possible to solve (\ref{eq:wavenumber}) on its own, but solving
(\ref{eq:wave_action2}) requires also the solution of (\ref{eq:wavenumber}).
In other words, the wave kinematics (the wavenumber distribution) are not
concerned with the wave action.
In contrast, the wave action is governed, among others, by the
group velocity and thus depends on the wavenumber.

@@

The first set of simulations is performed for the long-wave steepness of
$\varepsilon_L = 0.1$, $0.2$, and $0.4$ (Fig. \ref{fig:numerical_solutions}).
The long-waves are initialized from rest ($a_L = 0$) and gradually ramped up
to their target steepness over 5 long-wave periods, thus emulating the passage
of a long-wave group
(the importance of which we discuss in more detail in the next subsection).
At $\varepsilon = 0.1$, the numerical solutions for the wavenumber, amplitude,
and steepness modulation are all remarkably similar to the analytical solutions
(Fig. \ref{fig:numerical_solutions}a,d,g).
This suggests that at low long-wave steepness that the steady analytical solution
is a reasonable proxy for the fully-nonlinear crest-action conservation
equation solutions.
The numerical solutions diverge more notably from the analytical ones at
moderate steepness of 0.2 (Fig. \ref{fig:numerical_solutions}b,e,h), and are
considerably different at very high steepness of 0.4
(Fig. \ref{fig:numerical_solutions}c,f,i).
These differences suggest that at high steepness the inhomogeneity of
gravitational acceleration and group speed, otherwise ignored in the steady
solutions, become important.

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/numerical_vs_analytical_solutions_with_phase.png}
\caption{
  Comparison of numerical solutions (orange) of wavenumber (top), amplitude
  (middle), and steepness (bottom) modulation with their analytical solutions
  (blue), for $\varepsilon_L$ = 0.1, 0.2, and 0.4.
}
\label{fig:numerical_solutions}
\end{figure}

The maximum modulations of the short-wave wavenumber, amplitude, and steepness
from the analytical and numerical solutions, are shown on Figs.
\ref{fig:numerical_vs_analytical_k},
\ref{fig:numerical_vs_analytical_a}, and
\ref{fig:numerical_vs_analytical_ak}, respectively, as function of the long-wave
steepness $\varepsilon_L$.
Overall, the numerical solutions, based on the linear and the third-order Stokes
long waves alike, begin to diverge from the analytical solution at
$\varepsilon_L \approx 0.2$.
The numerical solution using the Stokes long wave is quantitatively very similar
to the fully-nonlinear solutions of \citet{longuet1987propagation} in amplitude
modulation, however with somewhat lower wavenumber and steepness modulations.
For example, at $\varepsilon_L = 0.4$, the steepness modulation in our solutions
is close to 6, whereas \citet{longuet1987propagation} finds it close to 8.
The underestimate in the wavenumber modulation at high long-wave steepness
relative to the results of \citet{longuet1987propagation}
is likely due to his long wave velocities being evaluated to a higher order in
$\varepsilon_L$ than they are here.
Nevertheless, the overall steepness modulation between the two numerical
approaches are remarkably similar, and either solution would cause the
short-waves of even low steepness to break \citep{banner1993wave}.
Where the two modulation solutions differ (at $\varepsilon_L > 0.2$),
either solution would lead to short-wave breaking after one long-wave period.
This suggests that in the cases where the short-waves would survive the
modulation and persist over multiple long-wave periods, the two solutions are
effectively equivalent.

@@

The key result of \citet{peureux2021unsteady} is that of unsteady steepening of
short waves when a homogeneous field of short waves is forced by an infinite
long-wave train.
The steepening is driven by the progressive increase in the action of short
waves (as opposed to their wavenumber), and is centered on the short-wave group
that begins its journey in the trough of the long wave.
This is because the unmodulated short waves that begin their journey in the
trough first enter the convergence region before reaching the divergence region.
Inversely, the short waves that begin around the crest of the long-wave first
enter the divergence region and will thus have their action and wavenumber
decreased.
We reproduce this behavior in Fig. \ref{fig:modulation_3panel_infinite}, which
shows the evolution of the short-wave action, wavenumber, and steepness
modulation (here defined as the change of a quantity relative to its initial value).
The long waves have $\varepsilon_L = 0.1$ and $k_L = 1$, and the short waves
have $k = 10$.
After 10 long-wave periods, the short-wave action is approximately doubled,
consistent with \citet{peureux2021unsteady}.
Another important property of this solution is that the short-wave group that
experiences peak amplification (dampening) are not locked-in to the long-wave
crests (troughs), as they are in the prior steady solutions
\citep{longuet1960changes,longuet1987propagation,zhang1990evolution}.

@@

Why does this unsteady growth of short-wave action occur?
\citet{peureux2021unsteady} explain that the change in advection velocity due to
the modulation of the short-wave group speed yields an additional amplification
of the short-wave action.
That is, the inhomogeneity term $N \dfrac{\partial C_g}{\partial x}$ is
responsible for the instability.
However, the instability only occurs if the short waves are initialized as a
uniform field.
If they are initialized instead as a periodic function of the long-wave phase
such that their wavenumber (and optionally, action) is higher on the crests
and lower in the troughs, akin to the prior steady solutions, the instability
vanishes and the short-wave modulation pattern locks-in to the long-wave
crests.

@@

Why is it, then, that the solution for short-wave modulation is not only
quantitatively, but also qualitatively, different depending on the short-wave
initial conditions?
It may at first seem that there is something special about the uniform initial
conditions that makes its solutions grow unsteadily and indefinitely.
\citet{peureux2021unsteady} described this scenario as "...the sudden appearance
of a long wave perturbation in the middle of a homogeneous short wave field".
However, such a scenario is not realistic in the ocean where waves tend to
organize into groups due to dispersion.
To test whether the sudden onset of long-wave forcing causes the unstable growth,
we repeat the numerical simulation of Fig.
\ref{fig:modulation_3panel_infinite}, except for a linear ramp applied to $a_L$
(and consequently, the other long-wave properties including the orbital
velocities and the local steepness) for the first five periods:
$a_L(t) = min(a_L, a_L t / \left(5 T_L\right))$, where $T_L$ is the long-wave period.
This result is shown in Fig. \ref{fig:modulation_3panel_ramp}.
The key distinction that arises with the introduction of the ramp is that the
modulation pattern of short waves is now locked-in to the long-wave crests,
and their indefinite steepening vanishes.
The stabilization effect of the long-wave ramp is more readily assessed in
Fig. \ref{fig:unsteady_growth_timeseries}, which shows the maximum short-wave
steepness modulation as function of time over 30 long-wave periods, for the
infinite long-wave train case and the case of applying a linear ramp.
Comparing the wave action propagation ($C_g \frac{\partial N}{\partial x}$) and
inhomogeneity ($N \frac{\partial C_g}{\partial x}$) tendencies reveals that
after only one long-wave period, the propagation and inhomogeneity tendencies
are unbalanced and amplify the steepening of short waves
(Fig. \ref{fig:inhomogeneity_tendencies}).
\citet{peureux2021unsteady} correctly pointed out that the unstable
growth of short-wave steepness occurs due to the resonance of the inhomogeneity
tendency with the short-wave action perturbation.
However, in the case of a gentle ramp-up of the long-wave forcing, the
propagation and inhomogeneity tendencies mostly balance each other and allow
the short-wave steepening to lock-in to the long-wave crests.

@@

We now proceed to examine the numerical solutions with the long-wave forcing
applied as a long-wave group.
The wave group is simulated as a non-dispersive train of long waves whose
amplitude scales with $\sin[\pi t / (n T_L)]$, where $n$ is the number of
long waves in the group.
The elevation of the long waves thus gradually ramps up from rest to $a_L$ at
$t = N/2 T_L$, after which it gradually decreases toward zero.
In this simulation, $n = 10$ and $\varepsilon_L = 0.1$ as in the previous two
simulations.
The modulations of short-wave wavenumber, amplitude, and steepness in response
to such long-wave group is shown in Fig. \ref{fig:modulation_3panel_groups}.
Like in the case of a linear ramp, the modulation pattern here is locked in to
the long-wave crest and peaks at approximately 1.2 for short-wave steepness.
After the peak of the long-wave group passes, the short-wave modulation recedes
back toward the resting state.

@@

The solutions presented here, analytical and numerical alike, are valid only
for certain scales of short and long waves.
Specifically, the wave action conservation equation, introduced by
\citet{bretherton1968wavetrains}, requires that the ambient velocity is slowly
varying on the time scales of short waves, \textit{i.e.}
$|\partial U / \partial x| \ll k |U|$
and $|\partial U / \partial t| \ll \sigma |U|$.
This implies $k_L \ll k$ and $|\sigma_L| \ll \sigma|$, respectively.
Another requirement is for the short-waves to remain linear, which implies
$a k \ll 1$.
Furthermore, the short waves examined here do not include the effects of
surface tension (gravity-capillary waves) or intermediate or shallow water
(although the solutions can be extended to those conditions, as
\citet{phillips1981dispersion} did, for example).
Within these limits, the crest-action conservation equations provide an
elegant and relatively simple framework to study the hydrodynamic modulation
of short waves by longer waves.
This approach, of course, isolates this particular process from other
dominant modulation and nonlinear transfer processes, such as wave growth
by wind, wave dissipation, and aerodynamic sheltering by the longer waves.

Although in this paper we only explored the solutions for $k_L = 1$ and $k=10$
the results are not sensitive to different values of $k_L$, provided that the
amplitude $a_L$ is set such that the long-wave steepness $\varepsilon_L = a_L / k_L$
is the same.
Numerical simulations with $k/k_L = 10$ and $k/k_L = 100$ show little
sensitivity to the ratio $k/k_L$ (not shown), consistent with the results of
\citet{longuet1987propagation}.
Specifically, the short-wave steepness modulation is 1\% larger at
$\varepsilon_L = 0.27$ for $k/k_L = 10$ compared to $k/k_L = 100$, and 4\%
larger at $\varepsilon_L = 0.4$.
This suggests that as long as $k/k_L \gg 1$, the modulation amplitude is
largely independent of the ratio $k/k_L$.
These results can be reproduced with the companion numerical model.

Despite several studies that provided qualitatively similar steady solutions
for the short-wave modulation by long waves
\citep{longuet1960changes,phillips1981dispersion,longuet1987propagation,henyey1988energy,zhang1990evolution},
it was not obvious from the governing equations that the fully-nonlinear
steady solutions should exist.
\citet{peureux2021unsteady} examined this problem numerically and found that
the solutions are stable only if the short-wave field is initialized from
a prior steady solution of the form of that from \citet{longuet1960changes}.
If the short-wave field is instead initialized from a uniform field, they
found that the short-wave amplitude, and thus steepness as well, grow
unsteadily.
However, here we demonstrate that the unsteady steepening of short
waves only occurs in the case of a sudden appearance of long waves, where
the velocity fields induced by the long waves act in their full capacity
on the short waves that have not yet had time to lock-in to the long-wave
crests.
In such a hypothetical scenario, sudden forcing on short waves causes the
modulation pattern to detach itself from the long-wave crests and to propagate
at the short-wave group speed.
When this occurs, the modulated short-waves are no longer in a stabilizing
resonance with the surface convergence and divergence induced by the long-wave
orbital velocity, and each long-wave passage further destabilizes the short-wave
field, causing it to steepen indefinitely.

Another important consideration of the hydrodynamic modulation process is
whether it should somehow be accounted for in phase-averaged spectral wave
models \citep{group1988wam,tolman1991third,donelan2012modeling} used for global
and regional wave forecasting.
Currently, most spectral wave models used for research or forecasting
do not consider the preferential steepening of short waves in the context
of their dispersion properties or the wind input
(\textit{i.e.} via the short-wave phase speed).
Some dissipation source functions use the cumulative mean squared slope
to quantify preferential dissipation of short waves due to this effect
\citep{donelan2012modeling,romero2019distribution}.
In the early days of spectral wave modeling, \citet{willebrand1975energy}
examined the effect of a wave spectrum on the short-wave group velocity,
and found the effect of up to several percent modulation.
For a practical implementation, this would incur an additional loop over all
frequencies longer than the considered short-wave frequency.
It was thus not deemed practical to include this effect in wave models at the time.
However, with the recent advances in computing power, machine learning for
acceleration of complex functions, and phase-resolved modeling of short waves,
considering the effect of wave-modulation beyond the simple cumulative mean
squared slope deserves re-examination.

@@

In this paper we revisited the problem of short-wave modulation by long waves
from a linear wave theory perspective.
Using the linearized wave crest and action conservation equations coupled with
nonlinear solutions for the effective gravity, we derived steady analytical
solutions for the modulation of short wave wavenumber, amplitude, steepness,
intrinsic frequency, and phase speed.
The latter two have not been previously examined in the context of short-wave
modulation, but may be important for correctly calculating the wind input into
short waves, which is proportional to the wind speed relative to the wave
celerity.
The approximate steady solutions yield higher wavenumber and amplitude
modulation than that of \citet{longuet1960changes}, and somewhat lower than 
the numerical solutions of \citet{longuet1987propagation} and
\citet{zhang1990evolution}.
This is mainly due to the analytical solution requiring the crest and action
conservation equations to be linearized, and the nonlinearity arising due
to the evaluation of short waves on the surface of the long wave (as opposed to
the mean water level) and due to nonlinear effective gravity.

The numerical solutions of the full wave crest and action conservation equations
are consistent with the analytical solutions for $\varepsilon_L \lesssim 0.2$.
The simulations also reveal that the unsteady growth of short-wave steepness
reported by \citet{peureux2021unsteady} is due to the sudden appearance of
long waves in a homogeneous short-wave field, a scenario that is unlikely to
occur in the open ocean.
A more likely condition such as that of a long-wave groups, are only mildly
destabilizing for the short waves.
These results suggest that for mildly-to-moderately steep short waves,
the analytical steady solutions presented here are sufficient to describe the
modulation of short waves by long waves.
It may be worthwhile to revisit a more systematic inclusion of the hydrodynamic
modulation effects in phase-averaged spectral wave models, beyond the simple
cumulative mean squared slope for wave dissipation, but also for modulating
the dispersion and wind input into short waves.
